Changes to police demand in COVID-19 pandemic

### 2022-03-24 docs/index.Rmd
Add table of newspaper headline screenshots
This includes cropping the Guardian screenshot to better fit the aspect ratio of the other images

class: center, middle
.pull-right[
![COVID19 and crime article](imgs/cov_news_01.png)
![COVID19 and crime article](imgs/cov_news_02.png)
]

.pull-left[
![COVID19 and crime article](imgs/cov_news_03.png)
![COVID19 and crime article](imgs/cov_news_04.png)
]

>>>>

class: center, middle

<table>
  <tr>
    <td><img src="imgs/cov_news_01.png" alt="Newspaper headline: 'This is too much': crime continues despite pandemic"></td>
    <td><img src="imgs/cov_news_02.png" alt="Newspaper headline: Exhausted cities face another challenge: a surge in violence"></td>
  </tr>
  <tr style="background-color: #FFFFFF;">
    <td><img src="imgs/cov_news_03.png" alt="Newspaper headline: Crime in UK falls sharply since start of coronavirus lockdown"></td>
    <td><img src="imgs/cov_news_04.png" alt="Newspaper headline: Crime rates drop across US amid the coronavirus pandemic"></td>
  </tr>
</table>
